### 2015-07-05 narrative/proposed-work.tex
added labels
edits

\underline{Principle 1:} A knowledge-centric system , let user knowledge  to define data policies. Today Storage System and I/O
layers are written in a stove-pipe fashion, and quite often don't allow optimizations to take place. We propose to re-design the
layer in a highly integrated fashion where user will place their intentions into the system and actions will dynamically and statically
take place to optimize for both the system and for individual requests.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be established so more science can be done on the
exascale Systems. Without predictable performance, the I/O layer performance must be guessed by the users, which quite often
mean that science is not performed well.

@@

%\input{narrative/qos-app}
\input{narrative/placement}
\input{narrative/migration}
\input{narrative/eviction-metrics}

>>>>

\underline{Principle 1:} A knowledge-centric system that allows user expertise to define data policies. Today Storage System and I/O
layers are written in a stove-pipe fashion and usually do not allow for optimizations. We propose to re-design this
layer in a highly integrated fashion that allows for user input. This re-designed layer will then statically, and dynamically optimize the use of resources for both the system and for individual users.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be established so more science can be done on the
exascale Systems. Unpredicitable performance in the I/O layer is often met with unpredictable guesses from users which decreases the effectiveness of simulation runs and the associated science.

@@

%\input{narrative/qos-app}
\input{narrative/placement}
% \input{narrative/migration}
% \input{narrative/eviction-metrics}
